\chapter{Conclusions and Recommendations}
\label{chp:conclusion}
\par This chapter summarizes the work and findings of this research. Section \ref{sec:research_conclusions} summarizes the conclusions reached. Section \ref{sec:research_impact} discusses the impact of this research. Section \ref{sec:future_work} provides recommendations for future work in the network address space randomization area in general and on \ac{ARG} itself.

\section{Research Conclusions}
\label{sec:research_conclusions}
\par This research demonstrates that \ac{IP} hopping is a suitable method of blocking unexpected external traffic while maintaining a minimal false-positive rate. This can be done completely transparently from the perspective of the internal and external hosts; the tool this thesis presents works with no configuration changes to any host other than the gateway.

\par In addition, \ac{ARG} proves rapid \ac{IP} address changes are possible, with network latency as the primary limiter. Tests demonstrate that---under this implementation---\ac{IP} addresses may change around 15 times per second (changes every 50 to 75 milliseconds) and still allow for reliable communication. 

\ac{ARG} also demonstrates good throughput, a critical aspect of usability to a real network. Test rates reach four \ac{Mbps} with no indication that \ac{ARG} is unable to handle greater rates. Running a fuzzer against \ac{ARG} found that, while gateways themselves remain stable in the face of malformed traffic, the attack may have an impact on connectivity and valid packet loss.

\section{Research Impact}
\label{sec:research_impact}
\par This thesis presents a new \ac{IP} address hopping tool that combines features of previous efforts in this area. Through a gateway-based solution, \ac{ARG} avoids requiring changes to existing network architecture or any clients inside. \ac{ARG} applies \ac{IP} address changes to all packets entering and leaving the network and packets between \ac{ARG}-protected networks include full encryption and authentication.

\par Of primary importance to this field of research is the demonstration that \ac{IP} address changes may occur multiple times per second. Previous research focuses on changes on the order of minutes or hours and may kill on-going connections when address changes occur. ARG's design allows for connections to persist across hops without participation of either end of the stream, ultimately allowing for much more frequent address changes and a potential amplification of the benefits of address space randomization.

\section{Future Work}
\label{sec:future_work}
\subsection{IPv6 Support}
\par \ac{IPv6} support is slowly becoming a requirement for any network system. For an \ac{IP} hopping system, \ac{IPv6} offers the benefit of a greatly increased address space, allowing systems to hop in a much broader range of addresses. \ac{ARG} is entirely \ac{IPv4} in its current implementation and cannot transport \ac{IPv6} packets to external hosts or to other gateways.

\subsection{Fragmentation Support}
\par \ac{ARG} currently has neither support for fragmenting packets as they pass through the gateway nor for notifying the sender that fragmentation is needed. Packets to and from external hosts pose no problem, as the original sender will handle this themselves. However, packets between gateways/\ac{ARG}-protected networks have additional data added, potentially exceeding the maximum transmission unit of the network. In this case, \ac{ARG} has no way to recover and the packet is permanently dropped without notice. A more complete implementation should notify the sender that fragmentation is needed.

\subsection{More Extensive Malicious Testing}
\par Due to time constraints, a full battery of robust malicious tests could not be performed against \ac{ARG}. As demonstrated by the basic fuzz testing, \ac{ARG} handles errors without becoming unstable, but may lose additional packets. The reasons behind this potential issue needs more exploration to determine the root cause and what should be done to fix it. More extensive work in both undirected (i.e., fuzz testing) and directed attacks is needed. For example, malicious hosts might attempt to falsely connect to a gateway or perform replay attacks in a more intelligent manner.  

%\subsection{Red teaming}
%\par In conjunction with the previous suggestion, 

\subsection{More Intelligent NAT}
\par \ac{ARG} currently blindly opens holes in the \ac{NAT} when it sees outbound packets and closes them after seeing no activity for a fixed amount of time. A transport layer examination would allow more fine-grained \ac{NAT} work, by watching for actual connection establishment and teardown packets. 

\subsection{Integration with Other Defenses}
\par Network defenses often perform better when working in tandem. \ac{ARG} has the potential to detect certain types of probes into the network. If this information can be passed off to an \ac{IDS}, it might alert an operator or take other defense actions on the network. In an even more active approach, \ac{ARG} might work with a honeypot to present a fake view of the network to an attacker. By examining what systems an attacker probes, it might be possible to determine the identity of the adversary, their goals, and their intended target in the network, all valuable information to those defending the network.

\subsection{Latency Compensation}
\par The current design of \ac{ARG} exhibits problems transferring packets when the hop interval is less than four times the latency. This situation is easy to detect, as latency between the gateways is already being calculated. To enable more flexibility with varying network conditions, gateways could change their hop interval on an individual basis to match the network conditions to every other gateway with which they connect. For example, say there are gateways \texttt{GateA}, \texttt{GateB}, and \texttt{GateC}. The latency between \texttt{GateA} and \texttt{GateB} is 50 ms, the latency between \texttt{GateB} and \texttt{GateC} is 40 ms, and the latency between \texttt{GateA} and \texttt{GateC} is 200 ms. By default, they each hop every 200 ms. When they perform time synchronization, \texttt{GateA} and \texttt{GateC} would detect the high latency and change the hop interval for \textit{just} each other to 600 ms, but leave their hop interval at 200 ms for \texttt{GateB}. 

\par Alternatively (or perhaps in addition), it would be possible to send packets with \ac{IP} addresses ``in the future,'' so that when they arrive at their destination the addresses would be current. That is, when a gateway is about to send a packet to another gateway, it calculates the addresses based on $\text{the current time} + \text{latency}$, rather than just the current time. This relies on network latency being relatively stable, as sudden drops in the latency would cause packets to contain future addresses when they arrive at the receiver. 

\section{Summary}
\par This chapter reviews the work and findings of this thesis. The impact of the research is discussed and recommendations for future work are given.

